```{r}
setwd("D:/Users/dia/Downloads/reproducible-research/RepData_PeerAssessment1")
```

---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---

## Loading and preprocessing the data
```{r}
actividad<-read.csv("activity.csv")
acumulado1<-aggregate(steps ~ date, actividad, sum)
acumulado2<-aggregate(steps ~ interval, actividad, mean)
```

## What is mean total number of steps taken per day?

```{r}
hist(acumulado1$steps,main="Histogram of Steps",xlab="Steps per day")
```

### Mean: 
```{r}
mean(acumulado1$steps)
```

### Median:
```{r}
median(acumulado1$steps)
```

## What is the average daily activity pattern?

```{r}
plot(acumulado2$interval,acumulado2$steps,type="l",ylab="Average of Steps",xlab="5 min Intervals of the Day",main="Time Series")
maximo<-acumulado2[acumulado2$steps==max(acumulado2$steps,na.rm = FALSE),]
```

### Maximum average of steps Interval
`r maximo$interval`

## Imputing missing values

```{r}
numna<-nrow(actividad[is.na(actividad$steps),])
```

### Number of missing values
`r numna`

```{r}
actividad2<-actividad
for (i in 1:nrow(actividad))
{
  if (is.na(actividad2$steps[i]))       
    actividad2$steps[i]<-acumulado2[acumulado2$interval==actividad$interval[i],2]
}
```

We filled the NA with the mean of the interval (from all the days)

```{r}
acumulado3<-aggregate(steps ~ date, actividad2, sum)
hist(acumulado3$steps,main="Histogram of Steps",xlab="Steps per day")
```

### Mean of the filled data: 
```{r}
mean(acumulado3$steps)
```

### Median of the filled data:
```{r}
median(acumulado3$steps)
```

#### Do these values differ from the estimates from the first part of the assignment?

We notice that the mean an median differ very little.

#### What is the impact of imputing missing data on the estimates of the total daily number of steps?

We notice that the histogram changes a bit because the sum has greater values.  But the average values don't change much.

## Are there differences in activity patterns between weekdays and weekends?

```{r}

```

